---
title: "R Notebook"
output: html_notebook
---

prereq:
install.packages("ggpolypath")


```{r}
library(readr)
library(ggpolypath)
library(ggplot2)
library(venn) 
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
setwd("D:/Shuting_Chen/mTBI_scRNA_seq/Jan12/DEGs_filtered_updown_sorted")

DEG_day1_aEC_up <- read_csv("./DEG_day1_aEC_up_sorted.csv")
DEG_day1_aEC_down <- read_csv("./DEG_day1_aEC_down_sorted.csv")
DEG_day1_capEC_up <- read_csv("./DEG_day1_capEC_up_sorted.csv")
DEG_day1_capEC_down <- read_csv("./DEG_day1_capEC_down_sorted.csv")
DEG_day1_vEC_up <- read_csv("./DEG_day1_vEC_up_sorted.csv")
DEG_day1_vEC_down <- read_csv("./DEG_day1_vEC_down_sorted.csv")

DEG_day1_acapEC_up <- read_csv("./DEG_day1_acapEC_up_sorted.csv")
DEG_day1_acapEC_down <- read_csv("./DEG_day1_acapEC_down_sorted.csv")
DEG_day1_vcapEC_up <- read_csv("./DEG_day1_vcapEC_up_sorted.csv")
DEG_day1_vcapEC_down <- read_csv("./DEG_day1_vcapEC_down_sorted.csv")


DEG_day3_aEC_up <- read_csv("./DEG_day3_aEC_up_sorted.csv")
DEG_day3_aEC_down <- read_csv("./DEG_day3_aEC_down_sorted.csv")
DEG_day3_capEC_up <- read_csv("./DEG_day3_capEC_up_sorted.csv")
DEG_day3_capEC_down <- read_csv("./DEG_day3_capEC_down_sorted.csv")
DEG_day3_vEC_up <- read_csv("./DEG_day3_vEC_up_sorted.csv")
DEG_day3_vEC_down <- read_csv("./DEG_day3_vEC_down_sorted.csv")

DEG_day3_acapEC_up <- read_csv("./DEG_day3_acapEC_up_sorted.csv")
DEG_day3_acapEC_down <- read_csv("./DEG_day3_acapEC_down_sorted.csv")
DEG_day3_vcapEC_up <- read_csv("./DEG_day3_vcapEC_up_sorted.csv")
DEG_day3_vcapEC_down <- read_csv("./DEG_day3_vcapEC_down_sorted.csv")


DEG_day7_aEC_up <- read_csv("./DEG_day7_aEC_up_sorted.csv")
DEG_day7_aEC_down <- read_csv("./DEG_day7_aEC_down_sorted.csv")
DEG_day7_capEC_up <- read_csv("./DEG_day7_capEC_up_sorted.csv")
DEG_day7_capEC_down <- read_csv("./DEG_day7_capEC_down_sorted.csv")
DEG_day7_vEC_up <- read_csv("./DEG_day7_vEC_up_sorted.csv")
DEG_day7_vEC_down <- read_csv("./DEG_day7_vEC_down_sorted.csv")

DEG_day7_acapEC_up <- read_csv("./DEG_day7_acapEC_up_sorted.csv")
DEG_day7_acapEC_down <- read_csv("./DEG_day7_acapEC_down_sorted.csv")
DEG_day7_vcapEC_up <- read_csv("./DEG_day7_vcapEC_up_sorted.csv")
DEG_day7_vcapEC_down <- read_csv("./DEG_day7_vcapEC_down_sorted.csv")
```


```{r}
setwd("/Users/iris/Downloads/DEGs_filtered_updown_sorted")

DEG_day1_allEC_up <- read_csv("./DEG_day1_allEC_up_sorted.csv")
DEG_day1_allEC_down <- read_csv("./DEG_day1_allEC_down_sorted.csv")
DEG_day3_allEC_up <- read_csv("./DEG_day3_allEC_up_sorted.csv")
DEG_day3_allEC_down <- read_csv("./DEG_day3_allEC_down_sorted.csv")
DEG_day7_allEC_up <- read_csv("./DEG_day7_allEC_up_sorted.csv")
DEG_day7_allEC_down <- read_csv("./DEG_day7_allEC_down_sorted.csv")
```



```{r}
x <- list(
  aEC = unique(c(DEG_day1_aEC_up$gene, DEG_day3_aEC_up$gene, DEG_day7_aEC_up$gene), c(DEG_day1_aEC_up$gene, DEG_day3_aEC_up$gene, DEG_day7_aEC_up$gene)), 
  vEC = unique(c(DEG_day1_vEC_up$gene, DEG_day3_vEC_up$gene, DEG_day7_vEC_up$gene)),
  capEC = unique(c(DEG_day1_capEC_up$gene, DEG_day3_capEC_up$gene, DEG_day7_capEC_up$gene))
  )
```

```{r}
x <- list(
  aEC_1 = unique(c(DEG_day1_aEC_up$gene, DEG_day3_aEC_up$gene, DEG_day7_aEC_up$gene)), 
  vEC_1 = unique(c(DEG_day1_vEC_up$gene, DEG_day3_vEC_up$gene, DEG_day7_vEC_up$gene)),
  capEC_1 = unique(c(DEG_day1_capEC_up$gene, DEG_day3_capEC_up$gene, DEG_day7_capEC_up$gene)),
  aEC_3 = unique(c(DEG_day1_aEC_up$gene, DEG_day3_aEC_up$gene, DEG_day7_aEC_up$gene)), 
  vEC_3 = unique(c(DEG_day1_vEC_up$gene, DEG_day3_vEC_up$gene, DEG_day7_vEC_up$gene)),
  capEC_3 = unique(c(DEG_day1_capEC_up$gene, DEG_day3_capEC_up$gene, DEG_day7_capEC_up$gene)),
  aEC_7 = unique(c(DEG_day1_aEC_up$gene, DEG_day3_aEC_up$gene, DEG_day7_aEC_up$gene)), 
  vEC_7 = unique(c(DEG_day1_vEC_up$gene, DEG_day3_vEC_up$gene, DEG_day7_vEC_up$gene)),
  capEC_7 = unique(c(DEG_day1_capEC_up$gene, DEG_day3_capEC_up$gene, DEG_day7_capEC_up$gene))
  )
```



```{r}
library(readr)
ucla_degs <- read_csv("D:\\Shuting_Chen\\code\\sc-mTBI\\ucla.degs.csv", skip = 2)

pv <- 0.05
fc <- 0.25

ucla_degs <- ucla_degs[ucla_degs$`Cell Type` == "Endothelial",]
ucla_degs <- ucla_degs[ucla_degs$Log.fold.change > fc | ucla_degs$Log.fold.change < -fc,]
ucla_degs <- ucla_degs[ucla_degs$`P Value` < pv,]
ucla_degs <- ucla_degs[(ucla_degs$Log.fold.change > 0 & ucla_degs$PCT.TBI > 0.1) | (ucla_degs$Log.fold.change < 0 & ucla_degs$PCT.Sham > 0.1),]
```





# each day
```{r}
x <- list(
  aEC = unique(c(DEG_day1_aEC_up$gene), c(DEG_day1_aEC_down$gene)),
  vEC = unique(c(DEG_day1_vEC_up$gene),c(DEG_day1_aEC_down$gene)),
  capEC = unique(c(DEG_day1_capEC_up$gene),c(DEG_day1_capEC_down$gene))
  )
```

```{r}
x <- list(
  aEC = unique(c(DEG_day1_aEC_up$gene), c(DEG_day1_aEC_down$gene)),
  vEC = unique(c(DEG_day1_vEC_up$gene),c(DEG_day1_aEC_down$gene)),
  capEC = unique(c(DEG_day1_capEC_up$gene),c(DEG_day1_capEC_down$gene)),
  acapEC = unique(c(DEG_day1_acapEC_up$gene),c(DEG_day1_acapEC_down$gene)),
  vcapEC = unique(c(DEG_day1_vcapEC_up$gene),c(DEG_day1_vcapEC_down$gene))
  )
```

```{r}
pdf("/Users/iris/Downloads/venn/day1.pdf")
#venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66"), sncs = 1.1, ilcs = 0.9)
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#f7cecc", "#9ccfe6", "#CCFF66", "#bdb5e1", "#f7b722"), sncs = 1.1, ilcs = 0.9)
dev.off()
```


```{r}
x <- list(
  aEC = unique(c(DEG_day1_aEC_up$gene), c(DEG_day1_aEC_down$gene)),
  vEC = unique(c(DEG_day1_vEC_up$gene),c(DEG_day1_aEC_down$gene)),
  capEC = unique(c(DEG_day1_capEC_up$gene),c(DEG_day1_capEC_down$gene)),
  UCLA = ucla_degs$Gene
  )
```

```{r}
pdf("day1+UCLA.pdf")
#venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66", "#CC99CC"), sncs = 1.1, ilcs = 0.9)
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#f7cecc", "#9ccfe6", "#CCFF66", "#bdb5e1", "#f7b722"), sncs = 1.1, ilcs = 0.9)

dev.off()
```


```{r}
x <- list(
  aEC = unique(c(DEG_day3_aEC_up$gene), c(DEG_day3_aEC_down$gene)),
  vEC = unique(c(DEG_day3_vEC_up$gene),c(DEG_day3_aEC_down$gene)),
  capEC = unique(c(DEG_day3_capEC_up$gene),c(DEG_day3_capEC_down$gene)),
  acapEC = unique(c(DEG_day3_acapEC_up$gene),c(DEG_day3_acapEC_down$gene)),
  vcapEC = unique(c(DEG_day3_vcapEC_up$gene),c(DEG_day3_vcapEC_down$gene))
  )
```

```{r}
pdf("/Users/iris/Downloads/venn/day3.pdf")
#venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66"), sncs = 1.1, ilcs = 0.9)
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#f7cecc", "#9ccfe6", "#CCFF66", "#bdb5e1", "#f7b722"), sncs = 1.1, ilcs = 0.9)
dev.off()
```

```{r}
x <- list(
  aEC = unique(c(DEG_day3_aEC_up$gene), c(DEG_day3_aEC_down$gene)),
  vEC = unique(c(DEG_day3_vEC_up$gene),c(DEG_day3_aEC_down$gene)),
  capEC = unique(c(DEG_day3_capEC_up$gene),c(DEG_day3_capEC_down$gene)),
  UCLA = ucla_degs$Gene
  )
```

```{r}
pdf("day3+UCLA.pdf")
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66", "#CC99CC"), sncs = 1.1, ilcs = 0.9)
dev.off()
```



```{r}
x <- list(
  aEC = unique(c(DEG_day7_aEC_up$gene), c(DEG_day7_aEC_down$gene)),
  vEC = unique(c(DEG_day7_vEC_up$gene),c(DEG_day7_aEC_down$gene)),
  capEC = unique(c(DEG_day7_capEC_up$gene),c(DEG_day7_capEC_down$gene)),
  acapEC = unique(c(DEG_day7_acapEC_up$gene),c(DEG_day7_acapEC_down$gene)),
  vcapEC = unique(c(DEG_day7_vcapEC_up$gene),c(DEG_day7_vcapEC_down$gene))
  )
```


```{r}
pdf("/Users/iris/Downloads/venn/day7.pdf")
#venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66"), sncs = 1.1, ilcs = 0.9)
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#f7cecc", "#9ccfe6", "#CCFF66", "#bdb5e1", "#f7b722"), sncs = 1.1, ilcs = 0.9)

dev.off()
```

```{r}
x <- list(
  aEC = unique(c(DEG_day7_aEC_up$gene), c(DEG_day7_aEC_down$gene)),
  vEC = unique(c(DEG_day7_vEC_up$gene),c(DEG_day7_aEC_down$gene)),
  capEC = unique(c(DEG_day7_capEC_up$gene),c(DEG_day7_capEC_down$gene)),
  UCLA = ucla_degs$Gene
  )
```


```{r}
pdf("day7+UCLA.pdf")
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#FFCC99", "#009999", "#CCFF66", "#CC99CC"), sncs = 1.1, ilcs = 0.9)
dev.off()
```

# allEC

```{r}
#use all EC
x <- list(
  UP_US = unique(c(DEG_day1_allEC_up$gene, DEG_day3_allEC_up$gene, DEG_day7_allEC_up$gene)),
  DOWN_US = unique(c(DEG_day1_allEC_down$gene, DEG_day3_allEC_down$gene, DEG_day7_allEC_down$gene)),
  UP_UCLA = ucla_degs[ucla_degs$Log.fold.change > 0,]$Gene,
  DOWN_UCLA = ucla_degs[ucla_degs$Log.fold.change < 0,]$Gene
  )
```

```{r}
# allEC
x <- list(
  UCLA = ucla_degs$Gene,
  TBI_Day1 = unique(c(DEG_day1_allEC_up$gene, DEG_day1_allEC_down$gene)),
  TBI_Day3 = unique(c(DEG_day3_allEC_up$gene, DEG_day3_allEC_down$gene)),
  TBI_Day7 = unique(c(DEG_day7_allEC_up$gene, DEG_day7_allEC_down$gene))
  )
```

```{r}
# capEC
x <- list(
  UCLA = ucla_degs$Gene,
  TBI_Day1 = unique(c(DEG_day1_capEC_up$gene, DEG_day1_capEC_down$gene)),
  TBI_Day3 = unique(c(DEG_day3_capEC_up$gene, DEG_day3_capEC_down$gene)),
  TBI_Day7 = unique(c(DEG_day7_capEC_up$gene, DEG_day7_capEC_down$gene))
  )

```


```{r}
pdf("mTBI_3days_withUCLA.pdf")
venn(x, ilab=TRUE, box = FALSE, ggplot = TRUE, size = 0, lty = "blank", zcolor = c("#CC99CC", "#f7cecc", "#9ccfe6", "#CCFF66"), sncs = 1.1, ilcs = 0.9)
dev.off()
```


# pairwise day
```{r}
x <- list(
  aEC_d1 = unique(c(DEG_day1_aEC_up$gene), c(DEG_day1_aEC_down$gene)),
  vEC_d1 = unique(c(DEG_day1_vEC_up$gene),c(DEG_day1_aEC_down$gene)),
  capEC_d1 = unique(c(DEG_day1_capEC_up$gene),c(DEG_day1_capEC_down$gene)),
  aEC_d3 = unique(c(DEG_day3_aEC_up$gene), c(DEG_day3_aEC_down$gene)),
  vEC_d3 = unique(c(DEG_day3_vEC_up$gene),c(DEG_day3_aEC_down$gene)),
  capEC_d3 = unique(c(DEG_day3_capEC_up$gene),c(DEG_day3_capEC_down$gene))
  )
```

```{r}
x <- list(
  aEC_d3 = unique(c(DEG_day3_aEC_up$gene), c(DEG_day3_aEC_down$gene)),
  vEC_d3 = unique(c(DEG_day3_vEC_up$gene),c(DEG_day3_aEC_down$gene)),
  capEC_d3 = unique(c(DEG_day3_capEC_up$gene),c(DEG_day3_capEC_down$gene)),
  aEC_d7 = unique(c(DEG_day7_aEC_up$gene), c(DEG_day7_aEC_down$gene)),
  vEC_d7 = unique(c(DEG_day7_vEC_up$gene),c(DEG_day7_aEC_down$gene)),
  capEC_d7 = unique(c(DEG_day7_capEC_up$gene),c(DEG_day7_capEC_down$gene))
  )
```

```{r}
x <- list(
  aEC_d1 = unique(c(DEG_day1_aEC_up$gene), c(DEG_day1_aEC_down$gene)),
  vEC_d1 = unique(c(DEG_day1_vEC_up$gene),c(DEG_day1_aEC_down$gene)),
  capEC_d1 = unique(c(DEG_day1_capEC_up$gene),c(DEG_day1_capEC_down$gene)),
  aEC_d7 = unique(c(DEG_day7_aEC_up$gene), c(DEG_day7_aEC_down$gene)),
  vEC_d7 = unique(c(DEG_day7_vEC_up$gene),c(DEG_day7_aEC_down$gene)),
  capEC_d7 = unique(c(DEG_day7_capEC_up$gene),c(DEG_day7_capEC_down$gene))
  )
```


# report shared

```{r}

Reduce(intersect, list(unique(c(DEG_day1_allEC_up$gene, DEG_day1_allEC_down$gene)), unique(c(DEG_day3_allEC_up$gene, DEG_day3_allEC_down$gene)), unique(c(DEG_day7_allEC_up$gene, DEG_day7_allEC_down$gene))))

Reduce(intersect, list(unique(c(DEG_day1_allEC_up$gene, DEG_day1_allEC_down$gene)), unique(c(DEG_day3_allEC_up$gene, DEG_day3_allEC_down$gene)), unique(c(DEG_day7_allEC_up$gene, DEG_day7_allEC_down$gene)), ucla_degs$Gene))

Reduce(intersect, list(DEG_day1_allEC_up$gene, DEG_day3_allEC_up$gene, DEG_day7_allEC_up$gene))
Reduce(intersect, list(DEG_day1_allEC_down$gene, DEG_day3_allEC_down$gene, DEG_day7_allEC_down$gene))
```

```{r}
# shared by 3 days
degs_usc <- Reduce(intersect, list(unique(c(DEG_day1_capEC_up$gene, DEG_day1_capEC_down$gene)), unique(c(DEG_day3_capEC_up$gene, DEG_day3_capEC_down$gene)), unique(c(DEG_day7_capEC_up$gene, DEG_day7_capEC_down$gene))))

# shared by 3 days + ucla
degs_usc_ucla <- Reduce(intersect, list(unique(c(DEG_day1_capEC_up$gene, DEG_day1_capEC_down$gene)), unique(c(DEG_day3_capEC_up$gene, DEG_day3_capEC_down$gene)), unique(c(DEG_day7_capEC_up$gene, DEG_day7_capEC_down$gene)), ucla_degs$Gene))

# up OR down
Reduce(intersect, list(DEG_day1_allEC_up$gene, DEG_day3_allEC_up$gene, DEG_day7_allEC_up$gene))
Reduce(intersect, list(DEG_day1_allEC_down$gene, DEG_day3_allEC_down$gene, DEG_day7_allEC_down$gene))
```


```{r}

```

